Regular singular Volterra equations on complex domains

### 2024-05-02 sima/reg-sing-volterra_sima.tex
Drop comment about integration path choice
Lower-case equation references

For simplicity, we use $\C$ as the position domain throughout this article. In the study of resurgence, however, the position domain is often a Riemann surface over $\C$, or even a more general ``translation surface.'' Thanks to our choice of formalism, our results and their proofs generalize immediately to this setting.
\subsubsection{Points and coordinates}
From now on, we will carefully respect the distinction between points and coordinates. A point is a location in space, while a coordinate is a function on space. For example, the position coordinates $\zeta$ and $\zeta_\alpha$ are functions on the position domain, just like the integral equation solutions $\psi_\alpha$. A coordinate, like $\zeta$, can be evaluated at a point $b$, yielding a number $\beta := \zeta(b)$. Conversely, the point $b$ can be described as the place where $\zeta = \beta$.
\subsubsection{Integration}
When we integrate, the integrand will always be either a 1-form, like $\varphi\,d\zeta$, or a density, like $|\varphi\,d\zeta|$. On a simply connected domain, all integration paths are equivalent, so we will typically specify an integral by its start and end points. These points may be given directly, as in the expression $\int_b^a \varphi\,d\zeta$, or described in terms of coordinates, as in the equivalent expression $\int_{\zeta = \beta}^a \varphi\,d\zeta$. When a bound depends on a particular choice of integration path, we will specify the path in the surrounding text. In the integral
\[ \int_{\zeta = \beta}^a \big(\zeta(a) - \zeta\big)^{-1/2} \varphi\,d\zeta, \]
notice that $\zeta(a)$ is a number, which stays constant throughout the integration, while $\zeta$ is a function, whose value changes along the integration path.
\subsubsection{Plugging into formal expressions}
Plugging a function $\varphi$ into a formal polynomial or power series $P$ gives a new function $P(\varphi)$. The correspondence between operators on the position and frequency domains will lead to expressions of this kind. In Section~\ref{sec:motivation}, for example, we saw that the differential operator $P\big(\tfrac{\partial}{\partial z}\big)$ on the frequency domain corresponds to multiplication by the function $P(-\zeta)$ on the position domain.\color{black}
\subsection{Notation}
\subsubsection{Uniform bounds}
Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we will write $|\varphi| \lesssim \omega$ to say that $|\varphi|$ is bounded by a constant multiple of $\omega$. Unless we say otherwise, the bound holds throughout the domain where both functions are defined. If the bound invovles an explicit variable, we will say that it holds over all values of the variable. For example, we will write ``$|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$'' to mean ``there is a constant $M$ such that for all $j \in \{0, 1, 2, \ldots\}$, the inequality $|R_j| \le M \lambda^j$ holds.''
\subsubsection{Boundary points}
A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}. If $\Omega \subset \C$ touches the $p \in \C$, we define a neighborhood of $p$ in $\Omega$ to be $U \cap \Omega$ for some open neighboorhood $U \subset \C$ of $p$. This agrees with the usual definition of a neighborhood when $p$ is an element of $\Omega$.

@@

\begin{proposition}\label{prop:smoothing}
Under {\em Condition~\eqref{cond:eps-lambda}}, the operator $\softpart$ maps
\[ \singexp{\sigma}{\Lambda}(\Omega) \to \singexp{\sigma+\gamma}{\Lambda}(\Omega) \]
continuously for all $\Lambda\geq \lambda_{\Delta}$ and $\sigma>-1$.
\end{proposition}
\begin{rmk}
We assume $\gamma > 0$, but this result holds even under the weaker assumption that $\gamma > -1$. We will take advantage of this in Section~\ref{sec:L-int-op}
\end{rmk}
\begin{proof}[Proof of Proposition~\ref{prop:smoothing}]
For any function $f\in\singexp{\sigma}{\Lambda}(\domain)$,
\begin{align*}
|\zeta(a)|^{-(\sigma+\gamma)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |f| \, |d\zeta| \\
&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
\end{align*}
By Condition~\eqref{cond:eps-lambda},
\begin{align*}
\int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\lesssim \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\gamma}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
&\lesssim |\zeta(a)|^{\gamma+\sigma} \int_{0}^1 (1-t)^\gamma e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
&\lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\gamma  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
&\lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\gamma  t^{\sigma}\;dt.
\end{align*}
The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. \textcolor{blue}{The integral on the last line is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so}
\[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}. \]
\textcolor{blue}{Since $\gamma > 0$ and $\sigma > -1$,} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
\[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
we conclude that $|\zeta(a)|^{-\sigma-\gamma} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\domain$. 
\end{proof}
\begin{corollary}\label{cor:pertub_f0}
Consider the prototype solution $\solproto$ from Equation~\eqref{eqn:test_solution}. If $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}, then $\softpart \solproto$ belongs to $\singexpalg{\tau-1+\gamma}(\domain)$.
\end{corollary}
\begin{proof}
We know from Theorem~\ref{thm:proto-growth} that $\solproto$ belongs to $\singexpalg{\tau-1}(\domain)$. Choose a constant $\Lambda \ge \lambda_\Delta$ big enough that $\solproto$ is in $\singexp{\tau-1}{\Lambda}(\domain)$. Since we are assuming $\tau$ is positive, we can apply Proposition~\ref{prop:smoothing}, concluding that $\softpart \solproto$ belongs to $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$.
\end{proof}
\subsection{Showing that $\volterra$ shrinks less singular functions \\ \textit{(toward Lemma~\ref{lem:perturbed_volterra})}}\label{sec:V is a contraction}
\subsubsection{Overview}
In this section, we will prove the following proposition. %We assume $\volterra$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:diag-basic} and \eqref{cond:eps-lambda}.

@@

To see that the fixed point is unique in the larger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$. Any fixed point in $\singexp{\rho-1}{\Lambda'}(\Omega)$ must map to the unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ under this inclusion. Next, observe that for any $\Lambda'' \ge \Lambda$, the map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda''}(\Omega)$. The inclusion $\singexp{\rho-1}{\Lambda}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda''}(\Omega)$ must send the unique fixed point in the smaller space to the unique fixed point in the larger one. Together, these arguments show that the fixed point is unique in $\singexpalg{\rho-1}(\Omega)$.
\end{proof}
\begin{proof}[Proof of Theorem~\ref{thm:general_volterra}]
Start with the prototype solution $\solproto$ constructed in Theorem~\ref{thm:basic_volterra}. The base point for the construction can be chosen arbitrarily. Under our assumptions about $\volterra$, Theorem~\ref{thm:proto-growth} ensures that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$. Our goal is to find a perturbation $\solptb \in \singexpalg{\tau-1+\gamma}(\domain)$ that makes $\solwhole = \solproto + \solptb$ a solution of 
\begin{equation}\label{eqn:orig-homog}
\solwhole = \volterra \solwhole.
\end{equation}
Observing that
\begin{align*}
\volterra \solproto & = \hardpart\solproto + \softpart\solproto \\
& = \solproto + \softpart \solproto,
\end{align*}
we rewrite the homogeneous equation we are trying to solve as an inhomogeneous equation for $\solptb$:
\begin{align}
\solproto + \solptb & = \volterra\solproto + \volterra\solptb \nonumber \\
& = \solproto + \softpart\solproto + \volterra\solptb \nonumber \\
\solptb & = \softpart\solproto + \volterra\solptb. \label{eqn:equiv-inhomog}
\end{align}
Since we know that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$, Proposition~\ref{prop:smoothing} shows that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\tau-1+\gamma}(\domain)$. Since $\tau+\gamma > \tau$, and we have made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\gamma}(\Omega)$. Equivalently, Equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\gamma}(\domain)$.
\end{proof}
\color{blue}\begin{proof}[Proof of Corollary~\ref{cor:expand_uniq}]
First, suppose $\rho \in (\tau, \tau+\gamma)$. In this case, the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} shows that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$. Lemma~\ref{lem:perturbed_volterra} then guarantees that equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\gamma}(\Omega)$.

@@

Our conditions on Volterra operators change to describe a regular singularity at $\zeta = \alpha$. For example, consider a Volterra operator $\hardpart^\alpha$ of the kind described in Section~\ref{setting:basic}, with kernel $\hardker^\alpha$. This operator now satisfies Condition~\eqref{cond:sing} if for some real, positive constant $\tau_\alpha$, the difference
\[ \hardker^\alpha(a, a) - \frac{\tau_\alpha}{\zeta(a) - \alpha} \]
is bounded on a neighborhood of $\zeta(a) = \alpha$ in $\domain_\alpha$, and for each $\sigma > \tau_\alpha$, the bound
\[ |\hardker^\alpha(a, a')| < \frac{\sigma}{|\zeta(a) - \alpha|} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha,\alpha)$ in $\domain_\alpha^2$. Condition~\eqref{cond:diag-basic} now requires that for some constant $\lambda_\Delta$,
\[|\hardker^\alpha(a,a')|\lesssim\frac{1}{|\zeta(a)-\alpha|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a,a'\in\domain_\alpha$. 
Similarly, an operator $\softpart^\alpha$ with kernel $\softker^\alpha$ now satisfies Condition~\eqref{cond:eps-lambda} if for some constants $\gamma > 0$ and $\lambda_\Delta$, we have
\[ |\softker^\alpha(a,a')| \lesssim \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)-\alpha|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain_\alpha$.
\subsection{The Laplace transform}
\subsubsection{Definition}
Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain \textcolor{blue}{$\zeta=\alpha$. Let} $\Gamma_{\zeta, \alpha}^\theta$ be the ray \textcolor{blue}{in the position domain} that leaves $\zeta=\alpha$ at angle $\theta$\textcolor{blue}{, and let $\Pi^{-\theta}_\Lambda$ be the half-plane $\Re(z e^{i\theta}) > \Lambda$ in the frequency domain.} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, \color{blue}the Laplace transform
\[ \laplace_{\zeta, \alpha}^{\theta} \maps \singexp{\sigma}{\Lambda}(\domain_\alpha) \to \holo(\Pi^{-\theta}_\Lambda) \]
is defined for all $\sigma > -1$ and $\Lambda \in \R$. Its action on a function $\varphi$ is given by the formula
\begin{equation}\label{laplace:int}
\laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
\end{equation}
\color{black}
\subsubsection{Action on integral operators}\label{sec:L-int-op}
For each $\nu \in (0, \infty)$, the fractional integral $\partial^{-\nu}_{\zeta, \alpha}$ is the Volterra operator defined by
\[ [\partial^{-\nu}_{\zeta, \alpha} \varphi](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} \varphi\;d\zeta \]
for each $a \in \domain_\alpha$. It obeys the semigroup law \cite[Section~1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{-\mu}{\zeta}{\alpha}\,\fracderiv{-\nu}{\zeta}{\alpha} & = \fracderiv{-\mu-\nu}{\zeta}{\alpha} & \mu, \nu \in (0, \infty),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer \cite[Equation~35]{mladenov2014advanced}.

>>>>

For simplicity, we use $\C$ as the position domain throughout this article. In the study of resurgence, however, the position domain is often a Riemann surface over $\C$, or even a more general ``translation surface.'' Thanks to our choice of formalism, our results and their proofs generalize immediately to this setting.
\subsubsection{Points and coordinates}
From now on, we will carefully respect the distinction between points and coordinates. A point is a location in space, while a coordinate is a function on space. For example, the position coordinates $\zeta$ and $\zeta_\alpha$ are functions on the position domain, just like the integral equation solutions $\psi_\alpha$. A coordinate, like $\zeta$, can be evaluated at a point $b$, yielding a number $\beta := \zeta(b)$. Conversely, the point $b$ can be described as the place where $\zeta = \beta$.
\subsubsection{Integration}
When we integrate, the integrand will always be either a 1-form, like $\varphi\,d\zeta$, or a density, like $|\varphi\,d\zeta|$. On a simply connected domain, all integration paths are equivalent, so we will typically specify an integral by its start and end points. These points may be given directly, as in the expression $\int_b^a \varphi\,d\zeta$, or described in terms of coordinates, as in the equivalent expression $\int_{\zeta = \beta}^a \varphi\,d\zeta$. In the integral
\[ \int_{\zeta = \beta}^a \big(\zeta(a) - \zeta\big)^{-1/2} \varphi\,d\zeta, \]
notice that $\zeta(a)$ is a number, which stays constant throughout the integration, while $\zeta$ is a function, whose value changes along the integration path.
\subsubsection{Plugging into formal expressions}
Plugging a function $\varphi$ into a formal polynomial or power series $P$ gives a new function $P(\varphi)$. The correspondence between operators on the position and frequency domains will lead to expressions of this kind. In Section~\ref{sec:motivation}, for example, we saw that the differential operator $P\big(\tfrac{\partial}{\partial z}\big)$ on the frequency domain corresponds to multiplication by the function $P(-\zeta)$ on the position domain.\color{black}
\subsection{Notation}
\subsubsection{Uniform bounds}
Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we will write $|\varphi| \lesssim \omega$ to say that $|\varphi|$ is bounded by a constant multiple of $\omega$. Unless we say otherwise, the bound holds throughout the domain where both functions are defined. If the bound invovles an explicit variable, we will say that it holds over all values of the variable. For example, we will write ``$|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$'' to mean ``there is a constant $M$ such that for all $j \in \{0, 1, 2, \ldots\}$, the inequality $|R_j| \le M \lambda^j$ holds.''
\subsubsection{Boundary points}
A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}. If $\Omega \subset \C$ touches the $p \in \C$, we define a neighborhood of $p$ in $\Omega$ to be $U \cap \Omega$ for some open neighboorhood $U \subset \C$ of $p$. This agrees with the usual definition of a neighborhood when $p$ is an element of $\Omega$.

@@

\begin{proposition}\label{prop:smoothing}
Under {\em Condition~\eqref{cond:eps-lambda}}, the operator $\softpart$ maps
\[ \singexp{\sigma}{\Lambda}(\Omega) \to \singexp{\sigma+\gamma}{\Lambda}(\Omega) \]
continuously for all $\Lambda\geq \lambda_{\Delta}$ and $\sigma>-1$.
\end{proposition}
\begin{rmk}
We assume $\gamma > 0$, but this result holds even under the weaker assumption that $\gamma > -1$. We will take advantage of this in Section~\ref{sec:L-int-op}
\end{rmk}
\begin{proof}[Proof of Proposition~\ref{prop:smoothing}]
For any function $f\in\singexp{\sigma}{\Lambda}(\domain)$,
\begin{align*}
|\zeta(a)|^{-(\sigma+\gamma)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |f| \, |d\zeta| \\
&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
\end{align*}
By Condition~\eqref{cond:eps-lambda},
\begin{align*}
\int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\lesssim \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\gamma}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
&\lesssim |\zeta(a)|^{\gamma+\sigma} \int_{0}^1 (1-t)^\gamma e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
&\lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\gamma  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
&\lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\gamma  t^{\sigma}\;dt.
\end{align*}
The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. \textcolor{blue}{The integral on the last line is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so}
\[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}. \]
\textcolor{blue}{Since $\gamma > 0$ and $\sigma > -1$,} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
\[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
we conclude that $|\zeta(a)|^{-\sigma-\gamma} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\domain$. 
\end{proof}
\begin{corollary}\label{cor:pertub_f0}
Consider the prototype solution $\solproto$ from equation~\eqref{eqn:test_solution}. If $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}, then $\softpart \solproto$ belongs to $\singexpalg{\tau-1+\gamma}(\domain)$.
\end{corollary}
\begin{proof}
We know from Theorem~\ref{thm:proto-growth} that $\solproto$ belongs to $\singexpalg{\tau-1}(\domain)$. Choose a constant $\Lambda \ge \lambda_\Delta$ big enough that $\solproto$ is in $\singexp{\tau-1}{\Lambda}(\domain)$. Since we are assuming $\tau$ is positive, we can apply Proposition~\ref{prop:smoothing}, concluding that $\softpart \solproto$ belongs to $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$.
\end{proof}
\subsection{Showing that $\volterra$ shrinks less singular functions \\ \textit{(toward Lemma~\ref{lem:perturbed_volterra})}}\label{sec:V is a contraction}
\subsubsection{Overview}
In this section, we will prove the following proposition. %We assume $\volterra$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:diag-basic} and \eqref{cond:eps-lambda}.

@@

To see that the fixed point is unique in the larger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$. Any fixed point in $\singexp{\rho-1}{\Lambda'}(\Omega)$ must map to the unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ under this inclusion. Next, observe that for any $\Lambda'' \ge \Lambda$, the map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda''}(\Omega)$. The inclusion $\singexp{\rho-1}{\Lambda}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda''}(\Omega)$ must send the unique fixed point in the smaller space to the unique fixed point in the larger one. Together, these arguments show that the fixed point is unique in $\singexpalg{\rho-1}(\Omega)$.
\end{proof}
\begin{proof}[Proof of Theorem~\ref{thm:general_volterra}]
Start with the prototype solution $\solproto$ constructed in Theorem~\ref{thm:basic_volterra}. The base point for the construction can be chosen arbitrarily. Under our assumptions about $\volterra$, Theorem~\ref{thm:proto-growth} ensures that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$. Our goal is to find a perturbation $\solptb \in \singexpalg{\tau-1+\gamma}(\domain)$ that makes $\solwhole = \solproto + \solptb$ a solution of 
\begin{equation}\label{eqn:orig-homog}
\solwhole = \volterra \solwhole.
\end{equation}
Observing that
\begin{align*}
\volterra \solproto & = \hardpart\solproto + \softpart\solproto \\
& = \solproto + \softpart \solproto,
\end{align*}
we rewrite the homogeneous equation we are trying to solve as an inhomogeneous equation for $\solptb$:
\begin{align}
\solproto + \solptb & = \volterra\solproto + \volterra\solptb \nonumber \\
& = \solproto + \softpart\solproto + \volterra\solptb \nonumber \\
\solptb & = \softpart\solproto + \volterra\solptb. \label{eqn:equiv-inhomog}
\end{align}
Since we know that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$, Proposition~\ref{prop:smoothing} shows that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\tau-1+\gamma}(\domain)$. Since $\tau+\gamma > \tau$, and we have made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\gamma}(\Omega)$. Equivalently, equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\gamma}(\domain)$.
\end{proof}
\color{blue}\begin{proof}[Proof of Corollary~\ref{cor:expand_uniq}]
First, suppose $\rho \in (\tau, \tau+\gamma)$. In this case, the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} shows that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$. Lemma~\ref{lem:perturbed_volterra} then guarantees that equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\gamma}(\Omega)$.

@@

Our conditions on Volterra operators change to describe a regular singularity at $\zeta = \alpha$. For example, consider a Volterra operator $\hardpart^\alpha$ of the kind described in Section~\ref{setting:basic}, with kernel $\hardker^\alpha$. This operator now satisfies Condition~\eqref{cond:sing} if for some real, positive constant $\tau_\alpha$, the difference
\[ \hardker^\alpha(a, a) - \frac{\tau_\alpha}{\zeta(a) - \alpha} \]
is bounded on a neighborhood of $\zeta(a) = \alpha$ in $\domain_\alpha$, and for each $\sigma > \tau_\alpha$, the bound
\[ |\hardker^\alpha(a, a')| < \frac{\sigma}{|\zeta(a) - \alpha|} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha,\alpha)$ in $\domain_\alpha^2$. Condition~\eqref{cond:diag-basic} now requires that for some constant $\lambda_\Delta$,
\[|\hardker^\alpha(a,a')|\lesssim\frac{1}{|\zeta(a)-\alpha|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a,a'\in\domain_\alpha$. 
Similarly, an operator $\softpart^\alpha$ with kernel $\softker^\alpha$ now satisfies Condition~\eqref{cond:eps-lambda} if for some constants $\gamma > 0$ and $\lambda_\Delta$, we have
\[ |\softker^\alpha(a,a')| \lesssim \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)-\alpha|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain_\alpha$.
\subsection{The Laplace transform}
\subsubsection{Definition}
Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain \textcolor{blue}{$\zeta=\alpha$. Let} $\Gamma_{\zeta, \alpha}^\theta$ be the ray \textcolor{blue}{in the position domain} that leaves $\zeta=\alpha$ at angle $\theta$\textcolor{blue}{, and let $\Pi^{-\theta}_\Lambda$ be the half-plane $\Re(z e^{i\theta}) > \Lambda$ in the frequency domain.} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, \color{blue}the Laplace transform
\[ \laplace_{\zeta, \alpha}^{\theta} \maps \singexp{\sigma}{\Lambda}(\domain_\alpha) \to \holo(\Pi^{-\theta}_\Lambda) \]
is defined for all $\sigma > -1$ and $\Lambda \in \R$. Its action on a function $\varphi$ is given by the formula
\begin{equation}\label{laplace:int}
\laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
\end{equation}
\color{black}
\subsubsection{Action on integral operators}\label{sec:L-int-op}
For each $\nu \in (0, \infty)$, the fractional integral $\partial^{-\nu}_{\zeta, \alpha}$ is the Volterra operator defined by
\[ [\partial^{-\nu}_{\zeta, \alpha} \varphi](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} \varphi\;d\zeta \]
for each $a \in \domain_\alpha$. It obeys the semigroup law \cite[Section~1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{-\mu}{\zeta}{\alpha}\,\fracderiv{-\nu}{\zeta}{\alpha} & = \fracderiv{-\mu-\nu}{\zeta}{\alpha} & \mu, \nu \in (0, \infty),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer \cite[equation~35]{mladenov2014advanced}.
